Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-01 manuscript/manuscript.tex
Continue writing manuscript

We computed the three gravity fields for different values of $D$, ranging from 1 to 10 with a step of 0.5 on every point of these four grids. Then, we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

>>>>

We computed the three gravity fields for different values of $D$, ranging from 0.5 to 10 with a step of 0.5 on every point of these four grids.
Then, we calculated the maximum difference between these results and the value of the analytical solution at the same height.

@@

To test the model in case of a exponential density we proposed the following function:

\begin{equation}
\rho(r') = A e^{-(r' - R)/b}
\end{equation}

\noindent where $A$ = 1 kg/m$^3$ and $b$ = 10$^6$ m.
